HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-17 paper/main.tex
www
Added alternative images for UCCA and HUME annotations

\begin{tikzpicture}[semithick, x=2.4cm,y=0.8cm, >=latex, baseline=7ex,
    inner sep=.3ex, outer sep=.7ex, minimum size=1.2ex,->]
  \node (ROOT) [fill=black, circle] {}
  child {node {After} edge from parent node[left]  {$L$\hspace{1.5cm}}}
  child {node (H1)  [fill=black,circle] {}
    child {node {graduation} edge from parent node[right] {$P$}}
      %child {node {to Paris} edge from parent node[right] {$A$}}
      edge from parent node[left] {$H$}
    }
    child {node (H2)  [fill=black,circle] {}
      child {node  {} edge from parent[draw=none]}
      child {node  {} edge from parent[draw=none]}
      child {node  (Tom) {Tom} edge from parent node[right] {$A$}}
      child {node  {moved} edge from parent node[right] {$P$}}
      child {node  [fill=black,circle] {}
        child {node  {to} edge from parent node[right] {$R$}}
        child {node  {NYC} edge from parent node[right] {$C$}}
        edge from parent node[right] {$A$}}
      %child {node {to Paris} edge from parent node[right] {$A$}}
      edge from parent node[left] {$H$}
    };
    \draw (H1) -> (Tom) node[midway, right] {$A$ \hspace{0.2cm}};
  \end{tikzpicture}
\caption{\label{fig:ucca_example}
  Sample UCCA annotation of the sentence ``After graduation, Tom moved
  to NYC''. Leaves correspond to words, whereas nodes correspond to units.
  Edge labels mark UCCA categories, which are largely ignored in this work.}
\end{figure}

@@

@@

\begin{figure*}[t]
    \begin{center}
    \includegraphics[width=1\textwidth]{hume_interface.png}
    \caption{The HUME annotation tool, based on the UCCA tool. The faded orange box at the top
      presents the translation, the large box below it presents the source. The tree of semantic units
      for the source is given underneath, where the aligned text appears in italics, and intervening words
      appear in red with a smaller font (e.g., in the first box).}
    \label{fig:interface}
    \end{center}
\end{figure*}

>>>>

\begin{tikzpicture}[semithick, x=2.4cm,y=0.8cm, >=latex, baseline=7ex,
    inner sep=.3ex, outer sep=.7ex, minimum size=1.2ex,->]
  \node (ROOT) [fill=black, circle] {}
  child {node {After} edge from parent node[left]  {$L$\hspace{1.5cm}}}
  child {node (H1)  [fill=black,circle] {}
    child {node {graduation} edge from parent node[right] {$P$}}
      %child {node {to Paris} edge from parent node[right] {$A$}}
      edge from parent node[left] {$H$}
    }
    child {node (H2)  [fill=black,circle] {}
      child {node  {} edge from parent[draw=none]}
      child {node  {} edge from parent[draw=none]}
      child {node  (Tom) {Tom} edge from parent node[right] {$A$}}
      child {node  {moved} edge from parent node[right] {$P$}}
      child {node  [fill=black,circle] {}
        child {node  {to} edge from parent node[right] {$R$}}
        child {node  {NYC} edge from parent node[right] {$C$}}
        edge from parent node[right] {$A$}}
      %child {node {to Paris} edge from parent node[right] {$A$}}
      edge from parent node[left] {$H$}
    };
    \draw (H1) -> (Tom) node[midway, right] {$A$ \hspace{0.2cm}};
  \end{tikzpicture}
\caption{\label{fig:ucca_example}
  Sample UCCA annotation of the sentence ``After graduation, Tom moved
  to NYC''. Leaves correspond to words, whereas nodes correspond to units.
  Edge labels mark UCCA categories, which are described in the table.}
%which are largely ignored in this work
\end{figure}

\begin{figure}
    \begin{center}
    \includegraphics[width=0.45\textwidth]{ucca-tree-v2.png}

\begin{tabular}{|l|l|l|l|}
\hline
L & Linker &  A & Participant \\
H & Scene & R & Relator \\
P & Process & C & Centre \\
\hline
\end{tabular}
    \end{center}
\caption{\label{fig:ucca_example_v2}
  Sample UCCA annotation where leaves correspond to words and nodes correspond to units.
  Edge labels mark UCCA categories, which are described in the table.}
%which are largely ignored in this work
\end{figure}

@@

\begin{figure}
    \begin{center}
    \includegraphics[width=0.45\textwidth]{ucca-tree-mteval-v2.png}
    \end{center}
  \caption{\label{fig:hume_tree_v2}
     HUME annotation of an UCCA tree with a word aligned example translation shown below. 
Atomic units are labelled using traffic lights and structural nodes are marked A or B.}
\end{figure}

In Figure~\ref{fig:hume_tree_v2} we can see an example of a possible HUME annotation, with the translation shown in English for ease of comprehension. When evaluating ``to NYC'' the annotator looks at the translation and sees the word ``stateside''. This word captures the whole phrase and so we mark the structural node with an atomic label. Here we choose ``Orange'' but the annotator could equally have decided that this translation is wrong and marked it as ``Red''. The ability to mark structural nodes with atomic labels allows the annotator to account for translations which only correspond at the phrase level. Another feature highlighted in this example is that the root node is ``Adequate''. This might seem confusing, as the relationship between the scenes has changed in the translation. However, an important feature of HUME is that penalises errors where they occur. In HUME, the error is caused by a wrong translation of the linker ``After'' which translates as ``by'' and this is marked as ``Red''. The root node still has two scene linked by one linker and there relationship between child nodes is maintained and therefore it is marked ``Adequate''. In HMEANT it is not clear whether errors should be propegated up the SRL hierarchy.

@@

\begin{figure*}[t]
    \begin{center}
    \includegraphics[width=1\textwidth]{hume_interface2.jpg}
    \caption{The HUME annotation tool, based on the UCCA tool. The faded orange box at the top
      presents the translation, the large box below it presents the source. The tree of semantic units
      for the source is given underneath, where the aligned text appears in italics, and intervening words
      appear in red with a smaller font (e.g., in the first box).}
    \label{fig:interface}
    \end{center}
\end{figure*}
